Workplan

### 2018-04-23 QualifyingReport/QualifyingReport.tex
added Qualifying Report
workplan updated

\begin{document}
	\section{Overview of Problem}
	\section{Literature Review}
	\section{Work already carried out}
	\section{Work Plan for the future}
	\section{Proposed Timetable}
	\section{Provision Table of Contents}
\end{document}

>>>>

\begin{document}
	\maketitle
	\newpage
	\section{Overview of Problem}
	I am interested in whether technology can be used to aid the early diagnosis of dementia specifically by analysing speech and language in a natural environment. As part of this, I am exploring the use of technologies such as the Amazon Echo or Google Home kit to capture speech and language. I am using Natural Language Processing to generate features from the captured speech such that we can categorise people into specific categories and/or predict test results on scores using machine learning.

	\section{Literature Review}

	\section{Work already carried out}

	\section{Work Plan for the future}

	\section{Proposed Timetable}
	\subsection{May 2019}

	\subsection{June 2019}

	\subsection{July 2019}

	\subsection{August 2019}

	\subsection{September 2019}

	\subsection{October 2019}

	\subsection{November 2019}

	\subsection{December 2019}

	\subsection{January 2020}

	\subsection{February 2020}

	\subsection{March 2020}

	\subsection{April 2020}

	\subsection{May 2020}

	\subsection{June 2020}

	\subsection{July 2020}

	\subsection{August 2020}

	\subsection{September 2020}

	\subsection{October 2020}

	\subsection{November 2020}

	\subsection{December 2020}

	\subsection{January 2021}

	\subsection{February 2021}

	\subsection{March 2021}

	\subsection{April 2021}
	\section{Provision Table of Contents}
\end{document}

### 2018-04-23 Workplan/Workplan.tex
workplan updated

\begin{document}
	\maketitle
	%\newpage
	\section{Interest Statement}
	I am interested in whether technology can be used to aid the early diagnosis of dementia specifically by analysing speech and language in a natural environment. As part of this, I am exploring the use of technologies such as the Amazon Echo or Google Home kit to capture speech and language. I am using Natural Language Processing to generate features from the captured speech such that we can categorise people into specific categories and/or predict test results on scores using machine learning.
	\section{Literature Review}
	\subsection{Dementia - Context}
	What is the Problem? 
	Why is this important?
	What is the potential impact?
	\subsection{How do Psychologists assess dementia}
	What tools do psychologists use to diagnose dementia? 
	Mini mental state examination (MMSE), 
	Addenbrooke's Cognitive Examination(ACE-III)
	(WAIS?)
	\subsection{How do Psychologists understand how language is affected by dementia}
	What language deficits are there and how are they characterised?
	What speech deficits are there and how are they characterised?
	\subsection{How is Natural Language Processing best positioned to help in this area?}
	\subsection{Are there any other technologies that can be used to help diagnosis?}

@@

	\subsection{Natural Language Processing}
	Online courses in Natural Language Processing
	Specific training in Natural Language Processing - Summer Schools?

@@

	\section{Proposed Timeline, Key Dates and Deliverables}
	\subsection{April 2018}
	Wednesday, 18th April - Workplan (First Draft Agreed)
	\subsection{May 2018}
	Wednesday, 9th May - Alexa Skills Training (All Day)
	\subsection{June 2018}
	Friday 15th June - First Draft of Literature to be handed in.
	Monday 18th June - Monday 25th June - Annual Leave
	\subsection{July 2018}

@@

	\subsection{February 2019}
	Friday, 1st February - Viva and Qualifying Report Due
\end{document}

>>>>

\begin{document}
	\maketitle
	\section{Interest Statement}
	I am interested in whether technology can be used to aid the early diagnosis of dementia specifically by analysing speech and language in a natural environment. As part of this, I am exploring the use of technologies such as the Amazon Echo or Google Home kit to capture speech and language. I am using Natural Language Processing to generate features from the captured speech such that we can categorise people into specific categories and/or predict test results on scores using machine learning.
	\section{Literature Review}
	\subsection{Dementia - Context}
	What is the Problem? 
	Why is this important?
	What is the potential impact?
	\subsection{How do Psychologists assess dementia}
	What tools do psychologists use to diagnose dementia? 
	Mini mental state examination (MMSE), 
	Addenbrooke's Cognitive Examination(ACE-III)
	Wechsler Adult Intelligence Scale(WAIS)
	The Free and Cued Selective Reminding Test (FCSRT)
	\subsection{How do Psychologists understand how language is affected by dementia}
	What language deficits are there and how are they characterised?
	What speech deficits are there and how are they characterised?
	\subsection{How is Natural Language Processing best positioned to help in this area?}
	\subsection{Are there any other technologies that can be used to help diagnosis?}

@@

	\subsection{Natural Language Processing}
	Online courses in Natural Language Processing

	\begin{itemize}
		\item Jurafsky and Martin - Speech and Language Processing 
		\item Manning and Schutze - Statistical NLP 
		\item Manning and Raghavan - Intro to IR
	\end{itemize}

@@

	\section{Proposed Timeline, Key Dates and Deliverables}
	\subsection{April 2018}
	Wednesday, 18th April - Workplan (First Draft Agreed)
	\subsection{May 2018}
	Wednesday, 9th May - Alexa Skills Training (All Day)
	\subsection{June 2018}
	Friday 15th June - First Draft of Literature Review to be handed in.
	\newline
	Monday 18th June - Monday 25th June - Annual Leave
	\subsection{July 2018}

@@

	\subsection{February 2019}
	Friday, 1st February - Qualifying Report Due

	\subsection{March 2018}

	\subsection{April 2018}
	Monday, 1st April - Viva Due by this point.
\end{document}
